---
title: "README"
output: 
  html_document:
    keep_md: true
---


```{r setup, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(DT)
```

## GitHub Documents
TEST2
This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## 데이터 불러오기

S-Dot 1시간 측정 평균값이 저장된 csv파일 read
```{r }
#분석하고자 하는 csv데이터를 sdot이라는 데이터 프레임에 넣기 
sdot<-read.csv("data/sdot_20200507.csv", fileEncoding = 'euc-kr', head=TRUE, check.names=FALSE) 

```


```{r, layout="l-body-outset"}
library(rmarkdown)
paged_table(sdot) %>% head(100)
```



sdot에 저장된 값에 대한 데이터 요약 
```{r }
#명령어 summary(데이터프레임)
summary(sdot) 



```
위의 값을 확인 했을때 미세먼지보정,초미세먼지 보정 등 최소 측정 값인 0을 벗어나는 음수(마이너스)값 확인 후 제거  

```{r }
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
